---
title: "linear model from Web"
author: "Julianne Mercado"
date: "fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

This scatter plot looks to be going more towards the right. So maybe it's a positive correlation. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```


### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation of a line is y=mx+b
The fit equation is SIMS=0.054563*ARM-4.095160

#### Predict at target point

SIMS=0.054563*88-4.095160

```{r}
0.054563*88-4.095160
```

My prediction to this would be 0.706384. Since we plugged in 88 into ARM and it resulted in 0.706384

```{r}
new <- data.frame(ARM = 88,GRIP = 94)
```

```{r}
predict(model.1,new, interval = "prediction")
```

#### scatterplot with model fit
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm) 
```

This would be the best fit for our data. Now we can see that when looking for an x-value of 88 and a y-value of 0.7 it's predicted that it fell into place. 

## Model 2 SIM~GRIP




### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

GRIP has a smaller correlation with SIMS vs ARM.

### Numerical results 
```{r}
cor(SIMS~GRIP, data=data)
```

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

If we look at the adjusted R squared value of this GRIP data, it is smaller than the ARM data adjusted R squared value. In addition, the residual standard error is larger for this grip data than the ARM data. Both of these values indicate that model 1 is a better model. 
#### predict model.2 at target point

```{r}
predict(model.2,new, interval = "prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basiccNN <- ggplot(data, aes(y=SIMS, x=GRIP))
basicNN + geom_point() + geom_smooth(method=lm)
```
   
   This is the results of the scatter plot and the best one for GRIP and SIMS data. If we use our prediction value.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP, data=data)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS ~ GRIP + ARM, data=data)
summary.lm(model.3)
```
SIMS= -5.43 + GRIP 0.02 + ARM * 0.04 



#### predict model.3 at target point
 
 
 Our residual standard error is 1.144 which is smaller than our other models, and our multiple R-squared is bigger, which makes this a bigger, which makes this a better fit model. SIMS 
```{r}
predict(model.3, new, interval = "prediction")
```


## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```


The model with GRIP and ARM is a better model than SIMS and ARM, we can see that from this anova function. 


### Model.2 vs Model.3
```{r}
anova(model.2,model.3)
```


Model 3 is a better model than model 2 because of the evidence that shows having less errors in model 3 than the other models. The values of RSS was 243.07 vs 188.43. 


## Informally compare Model.1 with model.2


```{r}
anova(model.1,model.2)
```

Model 1 has a smaller RSS of 217.88. We can say that Model 1 is the better model due to the less amount of errors. SIMS ~ ARM can be named the better model. 
